An Open Platform for Managing Short Programming Exercises

### 2013-06-25 paper/paper.tex
get rid of window decorations in screenshot
minor formatting/consistency change
avoid a redundancy

\begin{figure*}
\centering
\includegraphics[width=5.5in]{images/screenshot4}
\caption{Screenshot of the main view in CloudCoder}
\label{screenshot}
\end{figure*}

@@

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
of credits for Amazon Web Services\cite{aws} from Amazon,
which we plan to use to host CloudCoder directly for interested
institutions.  We are also investigating easier ways for
users to self-host. One possibility is enabling CloudCoder to run on application
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.

@@

In the Winter 2013 term at Knox College, students taking CS1 used {\tt CloudCoder}.
We collected over 6,000 submissions
for 32 exercises by 23 students.

>>>>

\begin{figure*}
\centering
\includegraphics[width=5.25in]{images/screenshot4}
\caption{Screenshot of the main view in CloudCoder}
\label{screenshot}
\end{figure*}

@@

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
of credits for Amazon Web Services\cite{aws},
which we plan to use to host CloudCoder directly for interested
institutions.  We are also investigating easier ways for
users to self-host. One possibility is enabling CloudCoder to run on application
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.

@@

In the Winter 2013 term at Knox College, students taking CS1 used CloudCoder.
We collected over 6,000 submissions
for 32 exercises by 23 students.
